The universal property of direct integrals in W$^*$-categories

### 2018-05-03 direct_integrals.tex
comment on the choice of measures

>>>>

\todo[inline]{Tob: I now think that the ``right'' definition may be in terms of \emph{semifinite} measures, by analogy with normal semifinite traces. My idea is that measurable families of objects are in some sense the objects of some ``$L^\infty(X,\cat{C})$'', which could perhaps be a W$^*$-category itself, along the lines of what Yetter~\cite{measureablecats} has proposed. This analogy with W$^*$-algebras makes me think that semifinite measures may be what we want}
